Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
minor edits

\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\

@@

\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,1\right\rbrace $ compute}\\

@@

\caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm. The lower bound, $\mathcal{Q}(\boldsymbol{\theta},\boldsymbol{\theta'})$, is maximized after each iteration to update the parameter estimates.}

@@

All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}. The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified. It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to the method proposed in \citet{Dewar2009}. This also suggests the use of an efficient algorithm to choose the minimum number of basis functions (states of the system) while achieving the desired details of the underlying field.  

@@

\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence and choose large values for $\mathbf P_t$ and $\mathbf M_t$} \\
\multicolumn{1}{|p{16cm}|}{Compute} \\

@@

\multicolumn{1}{|p{16cm}|}{Compute all the $n^2_x$ blocks of block matrices $\mathbf U$, $\Gamma_1$ and  $\Gamma_2$ using} \\

@@

\multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space model}\\
\multicolumn{1}{|p{16cm}|}{Compute all $n_x^2$ elements of $\boldsymbol\Lambda_{\theta}$ using} \\

@@

\multicolumn{1}{|p{16cm}|}{Compute transition matrix $\mathbf A(\boldsymbol\theta)$ } \\

@@

\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\hat{\mathbf x}_t^b$, the smoothed covariance,$\mathbf P^b_t$ and cross-covariance $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\  

@@

\multicolumn{1}{|p{16cm}|}{\textbf{5.} Convergence: go back to Step~2 unless }\\

>>>>

\multicolumn{1}{|p{16cm}|}{compute the filter gain, the filtered state and the filtered covariance matrix} \\

@@

\multicolumn{1}{|p{16cm}|}{for $t\in\left\lbrace T-1,\cdots,1\right\rbrace $ compute}\\

@@

\caption{\textbf{Algorithm for the RTS smoother (E-step).} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.}

@@

All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}. The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified. It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to the method proposed in \citet{Dewar2009}. This also suggests the use of an efficient algorithm to choose the minimum number of basis functions (states of the system) while achieving the desired details of the underlying field.  

@@

\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence $\hat{\mathbf X}$, and set $\mathbf P_t$ and $\mathbf M_t$ large} \\
\multicolumn{1}{|p{16cm}|}{compute} \\

@@

\multicolumn{1}{|p{16cm}|}{compute all the $n^2_x$ blocks of block matrices $\mathbf U$, $\Gamma_1$ and  $\Gamma_2$ using} \\

@@

\multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space representation}\\
\multicolumn{1}{|p{16cm}|}{compute all $n_x^2$ elements of $\boldsymbol\Lambda_{\theta}$ using} \\

@@

\multicolumn{1}{|p{16cm}|}{compute transition matrix $\mathbf A(\boldsymbol\theta)$ } \\

@@

\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\hat{\mathbf x}_t^b$, the smoothed covariance, $\mathbf P^b_t$ and cross-covariance, $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\  

@@

\multicolumn{1}{|p{16cm}|}{\textbf{5.} Convergence: return to Step~2 unless }\\
